10th International Satisfiability Modulo Theories Competition (SMT-COMP 2015): Rules and Procedures

### 2015-05-21 rules/rules15.tex
Pointed out new computation of accumulated run-time, which now takes unsolved benchmarks into account.
Main track post-processor renamed. Benchmarks that use bit-vector division excluded.

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  David D{\'e}harbe, Morgan Deters, Alberto Griggio, Albert Oliveras,
  Aaron Stump, and Tjark Weber.} describes the rules and competition
procedures for SMT-COMP~2015.  The principal changes from the previous
competition rules are the following:
\begin{itemize}
\item All solvers will be run with $n=4$ cores available.  We will
  recognize both best sequential and best parallel performance in all
  main track divisions, using different CPU time limits.
\item In addition to recognizing the best solver in each division, we
  will recognize solvers that perform best according to
  competition-wide criteria, emphasizing breadth of supported logics.
  These criteria will be a refinement of the criteria used for the
  FLoC Olympic Games medals in~2014.
\item We plan to include new divisions for floating-point arithmetic.
  These should be considered experimental in~2015, and will not be
  included in the competition-wide ranking.
\item We plan to run solvers on all eligible benchmarks.  Previous
  competitions used a proper subset of eligible benchmarks, causing
  competition results to be affected by a random selection process.
\end{itemize}

@@

The main track competition uses a StarExec postprocessor (named ``SMT2
results conserv") to accumulate the results.

@@

\header{Benchmark selection.}
%
The benchmark pool is culled as follows:
\begin{enumerate}
\item \emph{Retire inappropriate benchmarks.} The competition
  organizers may remove from the eligibility pool certain benchmarks
  that are inappropriate or uninteresting for competition, or cut the
  size of certain benchmark families to avoid their
  over-representation.
\item \emph{Eliminate benchmarks whose status is unknown.} Any
  benchmark whose expected output is neither {\tt sat} nor {\tt unsat}
  is removed.  There is a significant number of benchmarks with {\tt
    unknown} status in the library; these are certainly interesting
  and are a challenge to solve, but they are not used in the
  competition.\footnote{Incremental benchmarks may contain multiple
    \akey{check-sat} commands, each with its own status.  Incremental
    benchmarks that contain (some) \akey{check-sat} commands with {\tt
      unknown} status may still contain a prefix of commands where the
    status is known for all \akey{check-sat} commands in the prefix.
    This prefix is eligible for the application track.}
\end{enumerate}
%
All remaining benchmarks are used for the competition.  There will be
no further selection of benchmarks, e.g., based on benchmark
difficulty or benchmark category.

>>>>

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  David D{\'e}harbe, Morgan Deters, Alberto Griggio, Albert Oliveras,
  Aaron Stump, and Tjark Weber.} describes the rules and competition
procedures for SMT-COMP~2015.  The principal changes from the previous
competition rules are the following:
\begin{itemize}
\item All solvers will be run with $n=4$ cores available.  We will
  recognize both best sequential and best parallel performance in all
  main track divisions, using different CPU time limits.
\item The division scoring will take time spent on unsolved benchmarks
  into account.  Previous competitions only considered time spent on
  solved benchmarks.  However, the number of solved benchmarks still
  takes precedence over run-time.
\item In addition to recognizing the best solver in each division, we
  will recognize solvers that perform best according to
  competition-wide criteria, emphasizing breadth of supported logics.
  These criteria will be a refinement of the criteria used for the
  FLoC Olympic Games medals in~2014.
\item We plan to include new divisions for floating-point arithmetic.
  These should be considered experimental in~2015, and will not be
  included in the competition-wide ranking.
\item We plan to run solvers on all eligible benchmarks.  Previous
  competitions used a proper subset of eligible benchmarks, causing
  competition results to be affected by a random selection process.
\end{itemize}

@@

The main track competition uses a StarExec post-processor (named
``SMT-COMP 2015 Main Track Postprocessor") to accumulate the results.

@@

\header{Benchmark selection.}
%
The benchmark pool is culled as follows:
\begin{enumerate}
\item \emph{Retire inappropriate benchmarks.} The competition
  organizers may remove from the eligibility pool certain benchmarks
  that are inappropriate\footnote{In 2015, this (again) includes all
    benchmarks that use bit-vector division or remainder, because of
    an unresolved discussion about the semantics of division by zero.}
  or uninteresting for competition, or cut the size of certain
  benchmark families to avoid their over-representation.
\item \emph{Eliminate benchmarks whose status is unknown.} Any
  benchmark whose expected output is neither {\tt sat} nor {\tt unsat}
  is removed.  There is a significant number of benchmarks with {\tt
    unknown} status in the library; these are certainly interesting
  and are a challenge to solve, but they are not used in the
  competition.\footnote{Incremental benchmarks may contain multiple
    \akey{check-sat} commands, each with its own status.  Incremental
    benchmarks that contain (some) \akey{check-sat} commands with {\tt
      unknown} status may still contain a prefix of commands where the
    status is known for all \akey{check-sat} commands in the prefix.
    This prefix is eligible for the application track.}
\end{enumerate}
%
All remaining benchmarks are used for the competition.  There will be
no further selection of benchmarks, e.g., based on benchmark
difficulty or benchmark category.
